---
title: "Using mylm Package for Linear Regression"
author: "Your Name"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using mylm Package for Linear Regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(mylm)
library(bench)

```

Description: The mylm package provides a simple linear regression model function, my_lm, which allows the user to specify the regression formula and fit the model.

```{r setup}
set.seed(123)
data <- data.frame(
  x = rnorm(1000),
  y = 3 * rnorm(1000) + 5
)
model <- my_lm(y ~ x, data)
#model$coefficients
#model$fitted.values

```


model$coefficients: returns the estimated regression coefficients. For the example data, the coefficients should be close to an intercept of 1 and a slope of 2.


model$fitted.values: Returns the fitted values of the model, i.e. the predicted values given the independent variable x.


Comparison against the original R functions on simulated dataset to demonstrate correctness via all.equal()
```{r}
base_model <- lm(y ~ x, data)
#coef(base_model)
all.equal(as.vector(model$coefficients), as.vector(coef(base_model)), tolerance = 1e-8)
```


Comparison against the original R functions on simulated dataset to demonstrate efficiency via bench::mark()
```{r}
bench::mark(
  base_model = lm(y ~ x, data = data),
  model = my_lm(y ~ x, data = data),
  check = FALSE
)
```



